---
title: "Marriage License Statistics Report"
subtitle: "Analysis of Monthly Trends"
author: 
  - Your Name
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "This report analyzes monthly trends in marriage licenses issued at various civic centers. It aims to identify seasonal patterns and differences between civic centers."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

# Set a CRAN mirror (choose a mirror, e.g., USA)
options(repos = c(CRAN = "https://cloud.r-project.org"))

install.packages("here")
# Load the 'here' package (if already installed)
library(here)

library(tidyverse)
library(palmerpenguins)
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @opendatatorotno.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}


```{r}
#| label: fig-total-licenses
#| fig-cap: "Total Marriage Licenses Issued by Civic Center (2011-2024)"
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data %>%
  group_by(civic_centre) %>%
  summarize(total_licenses = sum(marriage_licenses, na.rm = TRUE)) %>%
  ggplot(aes(x = civic_centre, y = total_licenses, fill = civic_centre)) +
  geom_bar(stat = "identity", width = 0.6) +
  labs(title = "Total Marriage Licenses Issued by Civic Center (2011-2024)",
       x = "Civic Center",
       y = "Total Marriage Licenses") +
  theme_minimal() +
  theme(legend.position = "none")

```

The bar graph in Figure @ref(fig-total-licenses) illustrates the total number of marriage licenses issued by each civic center from 2011 to 2024. The Toronto civic center (TO) has issued significantly more marriage licenses compared to the other centers, which is likely due to its larger population and central role in the city. This disparity highlights the influence of geographic and demographic factors on marriage license issuance. Other civic centers, such as Etobicoke (ET), North York (NY), and Scarborough (SC), also show consistent activity, but at lower levels relative to Toronto. The variation across centers may reflect differences in population density, accessibility, and socio-economic factors in the regions served by these centers.




\newpage


# References


